---
title: "Wine EDA"
output: html_notebook
---
```{r}
knitr::opts_chunk$set(warning = F, results = T, message = F)
options(scientific=T, digits = 3) 

loadPkg = function(x) { if (!require(x,character.only=T, quietly =T)) { install.packages(x,dep=T,repos="http://cran.us.r-project.org"); if(!require(x,character.only=T)) stop("Package not found") } }
detach_package = function(pkg, character.only = FALSE) { if(!character.only) { pkg <- deparse(substitute(pkg)) } }
  search_item <- paste("package", pkg,sep = ":") 
  while(search_item %in% search()) { detach(search_item, unload = TRUE, character.only = TRUE) } 
  
loadPkg("ggplot2")
loadPkg("tidyverse")
loadPkg("dplyr")
```

```{r}
wine <- data.frame(read.csv("winemag-data_first150k.csv"))
```


# =============================================================================
# EDA Section 
#  Objectives: Learn about California wine country 
# =============================================================================

# -----------------------------------------------------------------------------
# Lets start off easy. Click on the dataframe in the global working 
# enviroment and get an idea of what you're working with. Alternatively 
# you can use functions like head(), summary(), and glipse() to do the 
# same thing
# -----------------------------------------------------------------------------
```{r}
glimpse(wine)
```


# -----------------------------------------------------------------------------
#From around the world, what countries are ranking above average and what countries are top 10 with the highest wine points?
# -----------------------------------------------------------------------------

```{r}
winecountry <- wine %>%
  group_by(country) %>%
  summarize(Average = mean(points))%>%
  arrange(desc(Average))
winecountry
top_n(winecountry, 10)

Total_winecountry_avg <- wine %>%
  group_by("country") %>%
  summarize(Average = mean(points))
Total_winecountry_avg

#TRYING TO GENERATE Above average wines
#explore_wine <- wine %>%
 # filter(winecountry > winecountry_avg)

```

# -----------------------------------------------------------------------------
# Worldwide, what wine has the highest rating? 
# Biased: What is the frequency of ratings by each country?
# -----------------------------------------------------------------------------

```{r}
winecountry <- wine %>%
  group_by(variety) %>%
  summarize(Average = mean(points))%>%
  arrange(desc(Average))
winecountry
top_n(winecountry, 10)

countryfreq <- wine %>%
  group_by(country) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
countryfreq
```


# -----------------------------------------------------------------------------
# Using the Top 10 countries, what wine has the highest rating?
# -----------------------------------------------------------------------------

```{r}
Top10_winerank <- wine %>%
  filter(winecountry) %>%
  group_by(variety) %>%
  summarize(Average = mean(points))
Top10_winerank
```

# -----------------------------------------------------------------------------
# What wine was reviewed most frequently?
# -----------------------------------------------------------------------------

```{r}
winefreq <- wine %>%
  group_by(variety) %>%
  summarize(count = n()) %>%
  arrange(desc(count))
winefreq
top_n(winefreq, 10)
```

# -----------------------------------------------------------------------------
# Use the filter() function to select wines grown in California. Assign the 
# output to the data frame ca_wine_reviews 
# -----------------------------------------------------------------------------
```{r}
ca_wine_reviews <- wine %>%
  filter(province == "California")%>%
  group_by(variety) %>%
  summarize(Average = mean(points))%>%
  arrange(desc(Average))
ca_wine_reviews 
```

# -----------------------------------------------------------------------------
# Now you know what wines are grown in California, but what are the most
# popular varities? Use the group_by() and summarize() functions to collapse 
# the ca_wine_reviews data frame and count the total number of wines grown 
# for each variety. Assign the output to the data frame ca_popular_wines 
# -----------------------------------------------------------------------------
```{r}
ca_popular_wines <- wine %>% 
  group_by(variety) %>% 
  summarize(count = n()) %>%
  arrange(desc(count))
ca_popular_wines
```
# -----------------------------------------------------------------------------
# We nearly have the answer to the question we're interested in 
# answering, what are the most popular varities in California? Use the 
# arrange() and slice() functions to return a data frame containing the 
# 10 most popular wines grown in Califonia. Asign the output to 
# ca_top_10. 
# -----------------------------------------------------------------------------
```{r}
ca_top_10 <- wine %>%
  filter(province == "California") %>%
  group_by(variety) %>%
  summarize(Average = mean(points))%>%
  arrange(desc(Average))
ca_top_10 
top_n(ca_top_10 , 10)
```
# Note: You might notice that the wines are not properly categorized. 
# We should consider a better procedure for grouping wine vareties in 
# the future. 

# Note: Notice this group of functions could easily answer many of 
# the questions we're interested in (e.g., what regions produce the best 
# wine? What wines is California best known for?) 

# -----------------------------------------------------------------------------
# Lets group vines by variety see if there's a relationship between 
# points and price 
# -----------------------------------------------------------------------------

Break down the wine market in California. What are the most popular wines grown in California? What regions/wineries in California produce the best wine? Are they close together? Do they grow the same varieties? 



What’s the distribution of wine prices in California? Is it skewed? Bimodal? What does this say about the typical wine consumer?


On average do California score better than wine from countries like France, Spain, and Italy? How about domestically, how do California wines stack up against the United States? 
