---
title: "Kaggle Wine EDA"
author: "by Data Wine'ing"
date: "3/5/2020"
output:
  html_document:
    code_folding: hide
    # number_sections: true
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r Preample, include = F}

# knitr settings 
knitr::opts_chunk$set(fig.width = 12, fig.height = 4,
  warning=FALSE, message=FALSE, echo = FALSE)

# set working directory 
setwd("~/Desktop/Git/edwinbet")

# load packages 
library(tidyverse, quietly = T)
library(gridExtra, quietly = T)
library(ggExtra, quietly = T)
library(kableExtra, quietly = T)
library(xtable, quietly = T)

# source files 
source("plotting_functions.R")

```

## 0. Raw Data 
***

```{r Data, include = F}
# load data 
raw_wine_reviews <- read.csv("data/winemag-data-130k-v2.csv")

# look at structure 
as.tibble(raw_wine_reviews)
```

### 0.1 First 10 Observations
```{r Glimpse, echo = F}
raw_wine_reviews %>%
  select(title, country, province, points, price) %>%
  setNames(c("Title", "Country", "Province", "Points", "Price")) %>% 
  slice(1:7) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F,
  position = "left")
```


##  1. Descriptive Statistic: Global Perspective 
***

```{r Descriptive statistics}

# Creat year variable 
wine_reviews <- raw_wine_reviews %>% 
  mutate(year = as.numeric(str_extract(title, "\\-*\\d+\\.*\\d*"))) %>% 
  mutate(year = ifelse(year > 1950 & year < 2017, year, NA))

# Summary statistics of  year, points, and price 
wine_reviews %>% 
  select(year, points, price) %>% 
  setNames(c("Year", "Points", "Price")) %>% 
  summary() %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F,
  position = "left")

```


## 2. Graphical Representation of Data & Normality Tests 
***

### Price 
```{r Normality tests I }
# Box Plot 
box <- wine_reviews %>%
  filter_outliers(price) %>% 
  wine_box(price, title = "Price", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  filter_outliers(price) %>% 
  wine_qq(price, "Price")

# Histogram 
hist <- wine_reviews %>% 
  filter_outliers(price) %>% 
  wine_hist(price, "Price", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)

```

### Year
```{r Normality tests II}
# Box Plot 
box <- wine_reviews %>%
  filter_outliers(year) %>% 
  wine_box(year, title = "Year", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  filter_outliers(year) %>% 
  wine_qq(year, "Year")

# Histogram 
hist <- wine_reviews %>% 
  filter_outliers(year) %>% 
  wine_hist(year, "Year", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)
```

### Points 
```{r Normality tests III}
# Box Plot 
box <- wine_reviews %>%
  filter_outliers(points) %>% 
  wine_box(points, title = "Points", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  filter_outliers(points) %>% 
  wine_qq(points, "Points")

# Histogram 
hist <- wine_reviews %>% 
  filter_outliers(points) %>% 
  wine_hist(points, "Points", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)
```


### Barplot of Wine Production
```{r Barplots }

top_10 <- wine_reviews %>%
  group_by(country) %>% 
  summarise(count = n()/ 129971) %>% 
  mutate(count = round(count, 2)) %>% 
  arrange(desc(count)) %>% 
  head(5) 

p1 <- ggplot(data = top_10, aes(x = reorder(country, -count), y = count), fill =
  country) +
  geom_bar(stat="identity",  fill = "#ffd1d1", col = "#811f1f") +
  labs(title = "Proportion of Total Wine Reviews \n by Country", 
  x = "Country", y = "Percentage") + ylim(0.0, 0.6) +
  geom_text(aes(label= count), vjust = -0.75, color="black" , size=3.5)+
  theme_minimal()

top_10 <- wine_reviews %>%
  filter(country == "US" & !province == "America") %>% 
  group_by(province) %>% 
  summarise(count = n()/ 54504) %>% 
  mutate(count = round(count, 2)) %>% 
  arrange(desc(count)) %>% 
  head(5) 

p2 <- ggplot(data = top_10, aes(x = reorder(province, -count), y = count), fill =
  province) +
  geom_bar(stat="identity",  fill = "#ffd1d1", col = "#811f1f") +
  labs(title = "Proportion of Total Wine Reviews \n in the US by State", 
  x = "State", y = "Percentage") + ylim(0.0, 0.8) +
  geom_text(aes(label= count), vjust = -0.75, color="black" , size=3.5)+
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```
 
 
## 3. Initial correlation / Chi Square tests / ANOVA analysis / Z-test or Z-interval / T-test or T-interval etc. 
***
 
### Bartlett Test Of Homogeneity Of Variances
```{r Bartlett}
# Bartlett 
big_wine <- wine_reviews %>% filter(country %in% c("Italy", "France", "US")) 
bartlett.test(big_wine$points, big_wine$country) 
```
 
### Overlayed Histagram
```{r Overlayed Histagram}
# Renamed variables 
wine_reviews <- wine_reviews %>% 
  mutate(region  = case_when(
    province == "California" ~ "California",
    country == "France" ~ "France", 
    country == "Italy" ~ "Italy"))

# Hist 
wine_reviews %>% 
  filter_outliers(price) %>%
  filter(!is.na(region)) %>% 
  ggplot(aes(x = points, colour = region)) +
  geom_density() + theme_minimal() + theme(text = element_text(size = 14),
  legend.position = c(0.8, 0.5)) + labs(title = "Distribution of Points by Region") 

``` 
 

### Anova 
Interpretation: The p-value is lower than the usual threshold of 0.05. You are confident to say there is a statistical difference between the groups
```{r Anova }
# subset 
big_wine <- wine_reviews %>% 
  filter(country %in% c("Italy", "France", "US")) 

# anova 
anova_results <- aov(points ~ country, data = big_wine)
summary(anova_results) 
```













## Correlation 

### Price vs. points 

Interpretation: Wines over \$300 dollars are typically >90pts, not suprising. However, There's a great variation in points among wines less that \$100. What counties in California produce the highest rated wines that cost less than \$50? 

```{r Correlation I}
# Scatter plot 
wine_reviews  %>% 
  filter(price < 500) %>% 
  ggplot(aes(x = price, y= points)) + 
  geom_point() +
  geom_smooth(method = lm, se = FALSE)

# Correlation points vs. price
cor.test(wine_reviews$price, wine_reviews$points)
```

### Price vs. years 

Interpretation: Not very fitted, does imply that the year a wine was produced has influence on how it's rated

```{r Correlation II}

# Remove Outliers 
IQR <- IQR(wine_reviews$price, na.rm = T)
Q <- quantile(wine_reviews$price, probs=c(.25, .75), na.rm = T)
lower_bound <- Q[1]- 1.5*IQR
upper_bound <- Q[2] + 1.5*IQR

# Scatter plot 
price_scatter <- wine_reviews %>% 
  filter(lower_bound < price & upper_bound > price & !is.na(price) & !is.na(year)) %>%
  ggplot(aes(x = year, y= price)) + 
  geom_count()  +
  geom_smooth(method = lm, se = FALSE)

# Correlation 
cor.test(wine_reviews$year, wine_reviews$points)
```

### Two Sample T 

Interpretation: The p-value is lower than the usual threshold of 0.05. You are confident to say there is a statistical difference between the groups

```{r Two sample t-test}
# subset  
domestic_wines <- wine_reviews %>% filter(country == "US")
imported_wines <- wine_reviews %>% filter(country != "US")

# t-test 
t.test(domestic_wines$points, imported_wines$points)
```





