---
title: "Kaggle Wine EDA"
author: "by Data Wine'ing"
date: "3/5/2020"
output:
  html_document:
    code_folding: hide
    # number_sections: true
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r Preample, include = F}

# knitr settings 
knitr::opts_chunk$set(fig.width = 12, fig.height = 4,
  warning=FALSE, message=FALSE, echo = FALSE)

# set working directory 
setwd("~/Desktop/Git/edwinbet")
source("eda_functions.R")

# load packages 
loadPkg(tidyverse)
loadPkg(gridExtra)
loadPkg(ggExtra)
loadPkg(kableExtra)
loadPkg(xtable)
loadPkg(gganimate)

```


```{r Data, include = F}
# load data 
raw_wine_reviews <- read.csv("data/winemag-data-130k-v2.csv")

# look at structure 
as.tibble(raw_wine_reviews)
```

<!-- ------------------------------------------------------------------
SLIDE 4
------------------------------------------------------------------ -->

### Glimpse of the Dataset
```{r Glimpse, echo = F}
raw_wine_reviews %>%
  select(title, country, province, points, price) %>%
  setNames(c("Title", "Country", "Province", "Points", "Price")) %>% 
  slice(1:7) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped", full_width = F,
  position = "left")
```

<!-- ------------------------------------------------------------------
SLIDES 5 - 7 
------------------------------------------------------------------ -->

###  Descriptive Statistics
```{r Descriptive statistics}

# Creat year variable 
wine_reviews <- raw_wine_reviews %>% 
  mutate(year = as.integer(str_extract(title, "\\-*\\d+\\.*\\d*"))) %>% 
  mutate(year = ifelse(year > 1950 & year < 2017, year, NA))

# Filter for outliers 
wine_reviews <- wine_reviews %>% 
  filter_outliers(price) %>% 
  filter_outliers(year) 

# Summary statistics of  year, points, and price 
wine_reviews %>% 
  select(year, points, price) %>% 
  setNames(c("Year", "Points", "Price")) %>% 
  summary() %>% 
  kable() %>% 
  kable_styling(bootstrap_options = "striped", full_width = F,
  position = "left")

```


### Graphical Representation of Price 
```{r Normality tests I }
# Box Plot 
box <- wine_reviews %>%
  wine_box(price, title = "Price", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  wine_qq(price, "Price")

# Histogram 
hist <- wine_reviews %>% 
  wine_hist(price, "Price", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)

```

### Graphical Representation of Year
```{r Normality tests II}
# Box Plot 
box <- wine_reviews %>%
  wine_box(year, title = "Year", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  wine_qq(year, "Year")

# Histogram 
hist <- wine_reviews %>% 
  wine_hist(year, "Year", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)
```

### Graphical Representation of Points  
```{r Normality tests III}
# Box Plot 
box <- wine_reviews %>%
  wine_box(points, title = "Points", fill = "#ffd1d1", col = "#811f1f")

# QQ Plot 
qq <- wine_reviews %>%
  wine_qq(points, "Points")

# Histogram 
hist <- wine_reviews %>% 
  wine_hist(points, "Points", bins = 12, fill = "#ffd1d1", col = "#811f1f")

lay <- rbind(c(1,2), c(1,3))
grid.arrange(grobs = list(hist, qq, box), layout_matrix = lay)
```

<!-- ------------------------------------------------------------------
SLIDE 5 - 8
------------------------------------------------------------------ -->

### Barplot of Wine Production
```{r Barplots }

top_10 <- wine_reviews %>%
  group_by(country) %>% 
  summarise(count = n()/ 129971) %>% 
  mutate(count = round(count, 2)) %>% 
  arrange(desc(count)) %>% 
  head(5) 

p1 <- ggplot(data = top_10, aes(x = reorder(country, -count), y = count),
  fill = country) +
  geom_bar(stat="identity",  fill = "#ffd1d1", col = "#811f1f") +
  labs(title = "Proportion of Total Wine Reviews \n by Country", 
  x = "Country", y = "Percentage") + ylim(0.0, 0.6) +
  geom_text(aes(label= count), vjust = -0.75, color="black" , size=3.5)+
  theme_minimal()

top_10 <- wine_reviews %>%
  filter(country == "US" & !province == "America") %>% 
  group_by(province) %>% 
  summarise(count = n()/ 54504) %>% 
  mutate(count = round(count, 2)) %>% 
  arrange(desc(count)) %>% 
  head(5) 

p2 <- ggplot(data = top_10, aes(x = reorder(province, -count), y = count),
  fill = province) +
  geom_bar(stat="identity",  fill = "#ffd1d1", col = "#811f1f") +
  labs(title = "Proportion of Total Wine Reviews \n in the US by State", 
  x = "State", y = "Percentage") + ylim(0.0, 0.8) +
  geom_text(aes(label= count), vjust = -0.75, color="black" , size=3.5)+
  theme_minimal()

grid.arrange(p1, p2, ncol = 2)
```
 
 <!-- ------------------------------------------------------------------
SLIDE 10
------------------------------------------------------------------ -->
 
### Bartlett Test Of Homogeneity Of Variance

```{r Bartlett}
# Bartlett 
big_wine <- wine_reviews %>% filter(country %in% c("Italy", "France", "US")) 
bartlett.test(big_wine$points, big_wine$country) 
```
 
### Overlayed Histagram

```{r Overlayed Histagram}
# Renamed variables 
wine_reviews <- wine_reviews %>% 
  mutate(region  = case_when(
    province == "California" ~ "California",
    country == "France" ~ "France", 
    country == "Italy" ~ "Italy"))

# Hist 
wine_reviews %>% 
  filter(!is.na(region)) %>% 
  ggplot(aes(x = points, colour = region)) +
  geom_density() + theme_minimal() + theme(text = element_text(size = 14),
  legend.position = c(0.8, 0.5)) + labs(title = "Distribution of Points by Region") + geom_vline(aes(xintercept= mean(points), color = region),
  linetype="dashed")

``` 


### Comparative Box Plots 
```{r}

# compare accross country
wine_reviews %>% 
  filter(!is.na(region)) %>% 
  ggplot(aes(x = region, y = points)) + 
  geom_boxplot(aes(color = region)) + 
  scale_color_manual(values = c("#00AFBB", "#E7B800", "#FC4E07")) + 
  theme_minimal()

# subset by group 
wine_reviews <- wine_reviews %>% 
 mutate(price_bucket = case_when(
   price < 15 ~ "less then $15",
   price %in% 15:29 ~ "$15 to $29",
   price %in% 30:44 ~ "$30 to $44", 
   price %in% 45:60 ~ "$45 to $60", 
   price > 60 ~ "greater than $60")
 ) %>% 
  mutate(price_bucket = factor(price_bucket, 
  levels = c("less then $15", "$15 to $29", "$30 to $44", 
    "$45 to $60", "greater than $60"))
  )

pallet <- c("#7A0177", "#C51B8A", "#F768A1", "#C51B8A","#7A0177")

# box plot by bucket 
ca <- wine_reviews %>% 
  filter(region == "California") %>% 
  ggplot(aes(x = price_bucket, y = points)) + labs(x = "California") +
  geom_boxplot(aes(col = price_bucket, fill = price_bucket, alpha = 0.15)) + 
  scale_color_manual(values = pallet) + scale_fill_manual(values = pallet) +
  theme_minimal() + theme(legend.position = "none")

it <- wine_reviews %>% 
  filter(region == "Italy") %>% 
  ggplot(aes(x = price_bucket, y = points)) + labs(x = "Italy") +
  geom_boxplot(aes(col = price_bucket, fill = price_bucket, alpha = 0.15)) + 
  scale_color_manual(values = pallet) + scale_fill_manual(values = pallet) +
  theme_minimal() + theme(legend.position = "none")

fr <- wine_reviews %>% 
  filter(region == "France") %>% 
  ggplot(aes(x = price_bucket, y = points)) + labs(x = "France") +
  geom_boxplot(aes(col = price_bucket, fill = price_bucket, alpha = 0.15)) + 
  scale_color_manual(values = pallet) + scale_fill_manual(values = pallet) +
  theme_minimal() + theme(legend.position = "none")

ca 
it 
fr

```

 
 
### Anova 

Interpretation: The p-value is lower than the usual threshold of 0.05. You are confident to say there is a statistical difference between the groups

```{r Anova }
# subset 
big_wine <- wine_reviews %>% 
  filter(country %in% c("Italy", "France", "US")) 

# anova 
anova_results <- aov(points ~ country, data = big_wine)
summary(anova_results) 
```

 <!-- ------------------------------------------------------------------
SLIDE 11
------------------------------------------------------------------ -->

### Two Sample T-Test 

```{r}

california <- wine_reviews %>% filter(province == "California") 
italy <-  wine_reviews %>% filter(country == "Italy")
france <-  wine_reviews %>% filter(country == "France")

# tests 
t.test(california$points, italy$points, var.equal = F) 
t.test(california$points, france$points, var.equal = F) 

# histograms 
p1 <- wine_reviews %>% 
  filter(region %in% c("France", "California")) %>% 
  ggplot(aes(x = points, colour = region)) +
  geom_density() + theme_minimal() + theme(text = element_text(size = 14),
  legend.position = c(0.8, 0.5)) + labs(title = "Distribution of Points by Region") + geom_vline(aes(xintercept= mean(points), color = region),
  linetype="dashed")

p2 <- wine_reviews %>% 
  filter(region %in% c("Italy", "California")) %>% 
  ggplot(aes(x = points, colour = region)) +
  geom_density() + theme_minimal() + theme(text = element_text(size = 14),
  legend.position = c(0.8, 0.5)) + labs(title = "Distribution of Points by Region") + geom_vline(aes(xintercept= mean(points), color = region),
  linetype="dashed")

grid.arrange(p1, p2, ncol = 1)
```

 <!-- ------------------------------------------------------------------
SLIDE 12
------------------------------------------------------------------ -->

### Regression Model 

```{r}

model <- wine_reviews %>%
  mutate(
    year_demeaned = year - 2011.146, 
    price_demeaned = price - 31.91123) %>% 
  filter(region %in% c("Italy", "France", "California")) %>% 
  lm(formula = points ~ region + price_demeaned + year_demeaned) 

summary(model) %>% 
  xtable() %>% 
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = "striped", full_width = F,
  position = "left")
```

<!-- ------------------------------------------------------------------
ADDITIONAL GRAPHICS
------------------------------------------------------------------ -->

### Scatter Plots
```{r}

# price  vs. points
wine_reviews %>%
  filter(region == "California") %>% 
  ggplot(aes(x = price, y = points)) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  geom_smooth(method=lm) +
  theme_minimal()

# price  vs. points grouped by region (not so informative)
wine_reviews %>%
  ggplot(aes(x = price, y = points, color = region)) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  geom_smooth(method=lm) + 
  theme_minimal()

# year  vs. points
wine_reviews %>%
  filter(region == "California") %>% 
  ggplot(aes(x = year, y = points)) +
  geom_point(show.legend = FALSE, alpha = 0.7) +
  geom_smooth(method=lm) + 
  theme_minimal()

```

### Animated Bar Plot 
```{r}
wine_reviews %>% 
  filter(!is.na(region)) %>% 
  group_by(region, year) %>% 
  summarise(count = n()) %>% 
  ggplot(aes(x = region, y = count, color = region, fill =
    region, alpha = 0.43)) + 
  geom_bar(stat="identity") + 
  transition_time(year) + 
  labs(title = "Year: {frame_time}") +
  theme_minimal() + 
  theme(legend.position = "none")
```




<!-- ------------------------------------------------------------------
END OF PRESENTATION 
------------------------------------------------------------------ -->

### Anova 

Recall our SMART research question **are wines grown in the New World (i.e., California) rated higher on average than wine grown in the Old World (i.e., France and Italy)**. To determine whether the average wine scores were the same between California, France, and Italy, we were interested in conducting a one way ANOVA test. Before doing so we attempted to validate each of the ANOVA assumptions of normality, homogeneity and independent errors. To visualize the distribution of points for each region we created a density plot displayed in **figure #**. Notice that each of the lines are approximately normal, verifying the first assumption. However, notice the points distribution in California is significantly flatter than Italy's. The Barlett's test displayed in **figure #** that the variance of wine scores among each region is different, violating the second ANOVA assumption. Furthermore, we believe in the existence of clustered errors in this dataset (e.g., scores of wines produced by the same vineyard are likely correlated). Since the ANOVA was no longer a viable option we opted to conduct a series of two-sample t-tests.

 [insert density plot] [insert Barretts test]

### Two-Sample T-Test 

We conducted two two-sample t-tests comparing California and Italy and California and France. Both the tests and their associated density plots are displayed in **figures # through #**. Both two-sample t-tests rejected the null hypothesis of equal means at the one percent level. Although the means are significantly different, the density plots reveal that the mean points of wines grown in each region are very similar, often within 0.1 points. Since the average wine score within each region is similar, this result suggests that the region where a wine is grown may not be a strong predictor of its wine score. 

[insert two sample t]
[inset density plots]

### Regression 

We estimate the following model to better understand the effect of the region where a bottle of wine is produced on the score of a bottle of wine holding other factors constant.

$$points = \beta_{0} + \beta_{1}*region + \beta_{2}*year + \beta_{3}*price + e$$ 

where points is equal to wine's score, region is equal to either California, France or Italy and price is measured in dollars. Both year and price are demeaned (i.e., the mean price and year have been subtracted from each observation in the sample) to easily interpret the intercept our model specification. Thus, we may interpret the intercept as the average score of a wine grown in California priced at roughly 32 dollars produced in 2011. The regression table is displayed in **figure #**. The region, year, and price variables are all statistically significant at the one percent level. Wines grown in France and Italy are rated 0.354 and 0.260 points higher than wines produced in California respectively. Also, the table suggests a one year increase in a wine's age is associated with a 0.176 point decrease in score. Similarly, a one-dollar increase in price is associated with a 0.097 increase in points. 

The model is consistent with similar statistics and figures discussed earlier in the paper and raise questions with regards to the effect of year on points. Similar to the two-sample t-test and box plots measuring points between California, Italy, and France, the regression table suggests that the region doesn't have a meaningful effect on wine scores when comparing the world's best wine regions. A 0.354 point increase in less than a one percent increase (form the average California wine with 88.3 points) and likely would not persuade a consumer exclusively interested in choosing wines based on points. Also, notice the coefficient   $\beta_{2}$ for $year$ is  positive. This result is surprising because aging, the process of storing wine before it is bottled, is associated with am improvement in taste and flavor over time. However, the coefficient suggests that wine produced in 2010 is roughly 2 points higher than wine produced in 1990 on average, which could be a meaningful difference for consumers. We look forward to building models with more of the variables available in our dataset and with other methods such as interaction terms, fixed effects, and difference and difference. 

[insert regression table]














